\begin{thebibliography}{9}

%%%%%%%%% ---------- Literature source
\bibitem{osinstall}
	OpenStack, \emph{OpenStack Installation Guide for Ubuntu 12.04/14.04 (LTS)}. 
	Online guide, 
	\url{http://docs.openstack.org/icehouse/install-guide/install/apt/content/}, 
	2014.

\bibitem{osconfref}
	OpenStack Foundation, \emph{OpenStack Configuration Reference}, 
	\url{http://docs.openstack.org/icehouse/config-reference/content/}, 
	2014.

\bibitem{osopsguide}
	OpenStack Foundation, \emph{OpenStack Operations Guide}. 
	Online book,
	\url{http://docs.openstack.org/openstack-ops/content/}, 
	2014.

\bibitem{osimgguide}
	OpenStack Foundation, \emph{OpenStack Virtual Machine Image Guide}. 
	Online guide,
	\url{http://docs.openstack.org/image-guide/content/}, 
	2014.

\bibitem{difallah14}
  Djellel E. Difallah and Pavlo, Andrew and Curino, Carlo and Philippe Cudr{\'e}-Mauroux,
  \emph{OLTP-Bench: An Extensible Testbed for Benchmarking Relational Databases}.
  Online article, \url{http://exascale.info/sites/default/files/p260-difallah.pdf}, 
  2014.

 \bibitem{tpcc10}
  Transaction Processing Performance Council (TPC),
  \emph{TPC BENCHMARK\textsuperscript{TM}C, Standard Specification}.
  Online article, \url{http://www.tpc.org/tpc_documents_current_versions/pdf/tpc-c_v5-11.pdf}, 
  2010.


%%%%%%%%% ---------- Web sources
\bibitem{cinder14}
  \emph{Laying Cinder Block (Volumes) In OpenStack, Part 1: The Basics}.
  \url{http://cloudarchitectmusings.com/2013/11/18/laying-cinder-block-volumes-in-openstack-part-1-the-basics/}, 
  Last visited: 12.07.2015.

\bibitem{network14}
  \emph{OpenStack Networking – FlatManager and FlatDHCPManager}.
  \url{hhttps://www.mirantis.com/blog/openstack-networking-flatmanager-and-flatdhcpmanager/}, 
  Last visited: 12.07.2015.


% %%%%%%%%% ---------- Citation source
\bibitem{cjanssen14}
	Cory Janssen,
	\emph{IT Infrastructure}, 
	\url{http://www.techopedia.com/definition/29199/it-infrastructure}, 
	Last visited: 15.09.2014.

\bibitem{osdef}
	OpenStack: The Open Source Cloud Operating System, 
	\url{http://www.openstack.org/software/}, 
	Last visited: 15.09.2014.

\bibitem{stodec}
	Storage Decisions, 
	\url{http://docs.openstack.org/openstack-ops/content/storage_decision.html}, 
	Last visited: 15.09.2014.

\bibitem{nist}
	Peter Mell and Timothy Grance, \emph{The NIST Definition of Cloud Computing}, 
	\url{http://csrc.nist.gov/publications/nistpubs/800-145/SP800-145.pdf}, 
	Last visited: 12.07.2015.



% %%%%%%%%% ---------- Figures source
\bibitem{osarch}
	Architecture, 
	\url{http://docs.openstack.org/icehouse/install-guide/install/apt/content/ch_overview.html}, 
	Last visited: 15.09.2014.


\end{thebibliography}